% --------------------------------------------------------------
% Preamble
% --------------------------------------------------------------

\documentclass[english,natbib,man,floatsintext]{apa6}
% \usepackage{arxiv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{url}            % simple URL typesetting
\usepackage{hyperref}       % hyperlinks
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{booktabs}       % professional-quality tables
\usepackage{tabularx}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{gensymb}        % degree, angle symbols
\usepackage{lscape} 

% for math equations and symbols
\usepackage{amsmath} 
\usepackage{amssymb}
\newcommand{\E}{\mathbb{E}}
\newcommand{\SD}{\mathit{SD}}
\newcommand{\SE}{\mathit{SE}}
\newcommand{\BF}{\mathit{BF}}
\DeclareMathOperator\arctanh{arctanh}

% This prevents placing floats before a section.
\usepackage{placeins}

% bibliography
%\usepackage{natbib}

% allows for floats when doing jou or doc style
\usepackage{graphicx}      
\graphicspath{{./Figures/}}  
\usepackage{threeparttable}
%\usepackage{float}

% for long tables
\usepackage{longtable}
% for multitables
\usepackage{multirow}
% to rotate figures
\usepackage{rotating}
% linenumbers
\usepackage[mathlines]{lineno}
\usepackage{pdflscape}

% in APA man mode captions are too large
% making sure they are reasonable
\usepackage{setspace}
% \usepackage[font=singlespacing]{caption}
% \captionsetup{font=singlespacing}

%%% some support for commenting
\usepackage{color}
\definecolor{Blue}{RGB}{0,0,255}
\definecolor{Red}{RGB}{255,0,0}
\definecolor{Green}{RGB}{0,255,0}
\newcommand{\jdc}[1]{\textcolor{Red}{[Jacob DC: #1]}}  
\newcommand{\jlo}[1]{\textcolor{Blue}{[Jacob O: #1]}} 
\newcommand{\spe}[1]{\textcolor{Green}{[Sonja: #1]}}

% ---------------------------------------------------------
% Title, authors
% ---------------------------------------------------------

\title{How (even imperfect preregistered) research can produce false positive findings}
\shorttitle{preregistered research and false positive findings}

\fourauthors{Jacob D. Christensen*}{Jacob L. Orquin}{Sonja Perkovic}{Carl-Johan Lagerkvist}
\fouraffiliations{Swedish University of Agricultural Sciences}{Aarhus University and Reykjavik University}{Aarhus University}{Swedish University of Agricultural Sciences}

\authornote{Jacob D. Christensen, *Correspondence concerning this article should be addressed to Jacob D. Christensen, Department of Economics at Swedish University of Agricultural Sciences. E-mail: jacob.dalgaard.christensen@slu.se.}

% ---------------------------------------------------------
% Abstract
% ---------------------------------------------------------

\abstract{Even with a small number of variables researchers can test many possible models of their data thus increasing the risk of false-positive results. Using combinatorics, we show that one key independent variable and three covariates can generate 95 possible models, while six covariates can generate over 2.3 million models. Such large model sets nearly guarantee false-positive findings. Using simulation, we show that preregistering a single analysis with a key independent variable heavily reduces the risk of false-positives. However, even so many models produce false-positive results with a much higher probability than the expected 5\%. The worst-case scenario are models with interactions between binary dummy coded variables and omitted main effects. Such models can generate false-positive results up to 41.9\% of the time. While preregistration is a crucial step towards reducing false-positive results, researchers need to carefully consider what analyses they preregister and we provide recommendations for what analyses to avoid. Our findings also suggest that interpreting p-values in exploratory analyses might be meaningless considering the high false-positive probability.
}

\keywords{type I error, false-positive statistics, replicability, simulation} 

\begin{document}
\maketitle

% introduction
\input{manuscript/introduction}

% method section
\input{manuscript/method}

% results section
\input{manuscript/results}

% discussion section
\input{manuscript/discussion}

% author contributions
\section{Author contributions}
JDC and JLO developed the study concept. JDC and SP performed the analyses. JDC, SP, CJL, and JLO wrote the manuscript. 

% data and code
\section{Data availability}
All code for simulation and figures in the paper can be found at \url{https://osf.io/2c5zw/}.

% reference list
\bibliographystyle{apalike}
\bibliography{references.bib}
\clearpage

% appendix
 \input{manuscript/appendix}

\end{document}